Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Comments

\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist?}
\maciek{Define $C^t$ to use once}
\maciek{"It can be easily verified"... True, but avoid such formulation. Something along these lines: if opt migrates earlier than t', then additionally pays for X, if later than Y.}
\maciek{"Thus, OPT pays ... which gives the competitive ratio" It is too early to give the competitive ratio if in the next paragraph we consider yet another case}

>>>>

\maciek{$\sigma_t$ undefined (I know what it is, though).}
\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist?}
\maciek{Define $C^t$ to use once}
\maciek{"It can be easily verified"... True, but avoid such formulation. Something along these lines: if opt migrates earlier than t', then additionally pays for X, if later than Y.}
\maciek{"Thus, OPT pays ... which gives the competitive ratio" It is too early to give the competitive ratio if in the next paragraph we consider yet another case. }
\maciek{Reason that the cost sharing between cases C1 and C3 is possible. Unclear to me, why every time C3 happens there must be a corresponding C1.}
